\chapter*{About the Author}
\addcontentsline{toc}{chapter}{About the Author}

When I was younger, I cursed God for my long, sleepless nights, nights
that seemed like days, days that seemed like months, not knowing if I
was male or female. But now I'm thankful to be non-binary, for it has
given me a creative edge, a humility, a sense of humor, the willingness
to listen to the rain, and a desire to help the marginalized. My
previous (nonfiction) book \emph{Rebuild: The Economy, Leadership, and
You,} offers a hopeful recipe for tackling our interconnected crises by
reimagining ourselves, our organizations, and our economies. Just like
being male and female has enabled me to become a more compassionate
human being, writing both fiction and nonfiction has enabled me to
become a better writer, teacher, listener, and parent. I live in Eau
Claire, Wisconsin, with my son Patrick, two cats, and a dog, where I
teach economics at the University of Wisconsin-Eau Claire.

\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

To my children, Elizabeth, and Patrick: our lives are forever
interconnected. Your zest for life vitalizes me and inspires me to make
the world better for you and your children. You have taught me so much.
I love your curiosity, humor, and compassion for diversity. My novel,
that you were forever (or at least so it seemed) inquiring when I would
finish, is finally in print!

Charles Wilber, Larry Marsh, and Chuck Craypo of the University of Notre
Dame, for believing in my fiction writing when no one else did.

The `lunch bunch' at the University of Notre Dame: Carol Wambeke,
Augusto de la Torre, Marie and Scott van der Linde. We came from
different parts of the world, connected, and became life-long friends.

Tim Crain, the first of my close friends to whom I confessed. We remain
close. Thanks!

Jeanne Charbonnet. We met by chance on a flight from Paris; two saucy
rebels who became spiritual soulmates. Thanks for being you! I'm glad
we're on the same journey!

Sharon Heinz: your counseling, wisdom, and belief in Jack Reardon gave
me hope during my darkest days.

My good friend and \emph{Rebuild} co-author Graham Boyd. A chance
meeting in London developed into a great friendship. I'm happy to say
that our second book is in the works.

And finally, the gang at Evolutesix, especially Johnny who did the
typesetting, and Niki who designed the cover. Thanks!
